Delta Smelt Enclosure Study 2019 Hybrid Paper Diet Analysis

### 2022-10-19 smelt_2019_allseasons/Diet 2019.Rmd
diet code updates

---
title: "Delta Smelt Enclosure Study 2019 Hybrid Paper Analysis"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

# load packages
```{r message=FALSE, warning=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
library(FSA)
```

# bring in contractor (UW) data
```{r}
diet2 <- read_csv("hybrid study/DSM Cage Diets 2019-2020.csv") #new data, not edited at all

@@

#remove DWSC
diet<-diet[diet$Location != "DWSC.Apr",]

@@

# plot number of empty stomachs
## these will not be included in the 100% stacked bar later
```{r}
#order locations
stomach_abundance$Location <- stomach_abundance$Location.x
stomach_abundance$Location <- ordered(stomach_abundance$Location, levels = c("RV.Feb", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))

@@

#order locations
prop$Location <- ordered(prop$Location, levels = c("RV.Feb", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))

>>>>

---
title: "Delta Smelt Enclosure Study 2019 Hybrid Paper Diet Analysis"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

# load packages
```{r message=FALSE, warning=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
library(FSA)
library(lubridate)
```

# bring in contractor (UW) data
```{r}
diet2 <- read_csv("smelt_2019_allseasons/data_raw/DSM Cage Diets 2019-2020.csv") #new data, not edited at all

@@

#remove DWSC
#diet<-diet[diet$Location != "DWSC.Apr",]

@@

# plot number of empty stomachs
## these will not be included in the 100% stacked bar later
```{r}
#order locations
stomach_abundance$Location <- stomach_abundance$Location.x
stomach_abundance$Location <- ordered(stomach_abundance$Location, levels = c("DWSC.Apr", "RV.Feb", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))

@@

#order locations
prop$Location <- ordered(prop$Location, levels = c("DWSC.Apr", "RV.Feb", "RV.Aug", "RV.Nov", "YB.Nov", "SM.Nov"))
